**Evalution of binary classification pipelines and methods for 16S rRNA gene data**

### 2018-11-14 submission/manuscript.Rmd
explain bxplot
clean up

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
######################################################################
#----------------- Read in necessary libraries -------------------#
######################################################################
deps = c("doParallel","pROC", "caret","knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
######################################################################
#-------------- Define the chunk options ----------------#
######################################################################
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
######################################################################
#-------------- Define knitr options to allow kable ----------------#
######################################################################
knitr::knit_hooks$set(inline=inline_hook)
options(kableExtra.latex.load_packages = FALSE)
options(kableExtra.auto_format = FALSE)
options(knitr.table.format = "latex")
library(kableExtra)
```

@@

**Figure 1. Generalization and classification performance of modeling methods ** AUC values of all cross validation and testing performances.
\begin{center}
\includegraphics[width=7in]{../results/figures/AUC_comparison.pdf}
\end{center}

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
######################################################################
#----------------- Read in necessary libraries -------------------#
######################################################################
deps = c("knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
######################################################################
#-------------- Define the chunk options ----------------#
######################################################################
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
```

@@

**Figure 1. Generalization and classification performance of modeling methods ** AUC values of all cross validation and testing performances. The boxplot shows quartiles at the box ends and the statistical median as athe horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges.
